### 2012-08-23 inst/examples/unmanaged_warning.Rmd
launched unmanaged warning, calibration step for issue #21

`ro tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, verbose=TRUE, cache=TRUE, cache.path="managed_warning/" or`

``` {r  echo=FALSE, cache=FALSE}
opts_knit$set(upload.fun = socialR::flickr.url)
options(device = function(width = 5, height = 5) {
    pdf(NULL, width = width, height = height)
})
````

>>>>

`ro tidy=FALSE, warning=FALSE, comment=NA, message=FALSE, verbose=TRUE, cache=TRUE, cache.path="unmanaged_warning/" or`

``` {r  echo=FALSE, cache=FALSE}
options(device = function(width = 5, height = 5) {
    pdf(NULL, width = width, height = height)
})
````
